---
title: "Lab 03 - Nobel laureates"
author: "Zi Li"
date: "Jan 29"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r}
as_tibble(nobel) 
glimpse(nobel)

nobel_living <- nobel %>%
  filter(!is.na(country))%>%  
           filter (gender != "org") %>%   
           filter (is.na(died_date))

glimpse(nobel_living)

# I found a useful answer for how to use filter commends on "stackoverflow"
```

# answer for Ex 1.1: we have 935 observations and 26 variables in this dataset; observations represented by rows and variables represented by collums. 
# answer for Ex 1.2:  my nobel_living left with a data frame with 228 observations and 26 variables. 

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
